Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-19 cav2017/cav2017.tex
review 2.7 Safety specifications for Cyber-Physical Systems

Finally, we also require that the closed-loop systems meets safety specifications. A safety specification establish bounds for the states, such that he controller $K$ must maintain the states within these bounds for any initial state.

The safety property (represented by $\phi_{safety}$) is encoded as follows:
\begin{equation}
\label{eq:safetyliteral}
\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{x_{i}^{-} \leq x_{i,k} \leq x_{i}^{+}},
\end{equation}
where $x_{i}^{-}$ and $x_{i}^{+}$ are respectively the lower and upper bound of the $i$-th state $x_{i}$ at the $k$-th instant, i.e., the states will always be within the $n$-dimensional hyperbox defined by the safety specifications (bounds).

The closed-loop state-space system have to be unrolled until a specific depth ($k_{bound}$) to ensure $\phi_{safety}$. The limit $k_{bound}$ is the number of iterations sufficient so that the rate of variation (derivative) of the states is negligible ensuring the boundaries will not be violated for any $k>k_{bound}$. \commentib{The k-bound estimative must be explained.}

For any $k\leq k_{bound}$ the states must be computed considering the FWL effects in all operations related to the control action~\ref{eq:controlaction} and disregarding it in the state equation ~\eqref{eq:plant}. Thus, the states are computed using the following equations:
\begin{equation}
\label{eq:ssunroll}
\left\lbrace
\begin{array}{l}
u_{k}=\mathcal{F}_{\langle I,F \rangle}(r_{k}-\mathcal{F}_{\langle I,F \rangle}(\mathcal{F}_{\langle I,F \rangle}(K)\cdot\mathcal{F}_{\langle I,F \rangle}(x_{k})))\\
x_{k+1}=Ax_{k}+Bu_{k}
\end{array}\right.
\end{equation}

>>>>

We require that the closed-loop system meets safety specifications. 
A safety specification establishes bounds for the states, such that 
the controller $K$ must maintain the states within a given lower and upper 
bound for any initial state.

The safety property represented by $\phi_{safety}$ is encoded as follows:
%
\begin{equation}
\label{eq:safetyliteral}
\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{x_{i}^{-} \leq x_{i,k} \leq x_{i}^{+}},
\end{equation}
%
where $x_{i}^{-}$ and $x_{i}^{+}$ are the lower and upper bound 
of the $i$-th state $x_{i}$ at the $k$-th instant, respectively.
This means that the states will always be within the $n$-dimensional 
hyper-box, which is typically defined by the safety specification.

The closed-loop state-space system has to be unwound up to a given 
depth $k_{bound}$ to ensure that $\phi_{safety}$ holds. 
Here, $k_{bound}$ represents the number of iterations 
to sufficiently unwind the closed-loop state-space system 
so that the variation rate (derivative) of the states is negligible, 
ensuring that the boundaries are not be violated for any $k>k_{bound}$. 
\commentib{The k-bound estimation must be explained.}

For any $k\leq k_{bound}$, the states must be computed considering 
the FWL effects in all operations related to the control action~\eqref{eq:controlaction} 
and disregarding it in the state equation~\eqref{eq:plant}. 
Thus, the states are computed using the following equations:
%
\begin{equation}
\label{eq:ssunroll}
\left\lbrace
\begin{array}{l}
u_{k}=\mathcal{F}_{\langle I,F \rangle}(r_{k}-\mathcal{F}_{\langle I,F \rangle}(\mathcal{F}_{\langle I,F \rangle}(K)\cdot\mathcal{F}_{\langle I,F \rangle}(x_{k})))\\
x_{k+1}=Ax_{k}+Bu_{k}
\end{array}\right.
\end{equation}
